---
title: "Milestone 3"
author: "Liz Masten"
date: "2/19/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(foreign)
library(gt)
library(tinytex)
library(tidyverse)

```

```{r data}

#read in data: 

data <- read.dta("fpy_replication_data_jop_2012.dta")


```

Games Rival's Play: Terrorism in International Rivalries

Michael Findley, James Piazza, and Joseph Young argue in their paper Games Rivals Play: Terrorism in International Rivalries that interstate rivalries are a positive predictor of transnational terrorist activity. In other words, terrorist attacks are more likely to occur in the context of a rivalry between two states than in the absence of such a rivalry. They empirically test their hypothesis by analyzing “politically relevant directed state dyads,” meaning that they focus on country-level factors in states that sponsor terrorism as well as target states, while ignoring the states that are unlikely to interact at all in the international system. This use of politically relevant dyads allows the authors to incorporate covariates (rivalry, joint democracy, contiguity, and capability ratio) as controls, as well as practice good statistical practices by discounting irrelevant dyads that would increase the number of observations, thus increasing the likelihood of spurious statistical significance. 


